The Name of the Title is Hope

### 2020-03-18 paper.tex
More figs
Some stuff in methods

%%
%% This is file `sample-sigchi.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigchi')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigchi.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigchi]{acmart}

@@

% Ecological Validity:
% Why does your study answer your research question? Why
% does your evaluation address your hypothesis? Make sure your study, and the
% variables you're measuring, properly address the question you are asking.
\begin{figure*}[ht]
  \centering
  \includegraphics[width=\textwidth]{results/task_points.png}
  \caption{
    Examples did not noticeably affect time-to-completion, except in Task 2
    where the effect is dramatic.
  }
  \label{fig:data-points}
\end{figure*}

\section{Results}
% Figures.
% Analysis
\section{Discussion}

>>>>

\RequirePackage[hyphens]{url}
\documentclass[sigchi]{acmart}
%% Include the standard set of goodies
\include{builtins/std}

@@

% Ecological Validity:
% Why does your study answer your research question? Why
% does your evaluation address your hypothesis? Make sure your study, and the
% variables you're measuring, properly address the question you are asking.
\subsection{Measures}
% We expected to see that examples increased the speed of candidate selection
% with little to no loss in accuracy.
% %
% Furthermore we expected that speedup to be explained by decreased reliance on
% the interpreter.
% %
% Specifically, users should no longer need to run their own input-output tests
% on the candidate programs.

For each participant, we measured:
\begin{itemize}
    \item Time-to-correct solution (per task)
    \item Count of incorrect guesses (per task)
    \item Count and type of interpreter queries (across all tasks)
\end{itemize}

The first metric directly tests the hypothesis that examples improve
selection speed, but the result could be misleading if there was also a
change in selection accuracy.
%
Counting incorrect guesses ensures that any such change is captured.
%
Beyond assessing the effectiveness of examples, measuring how often and why
participants used the interactive interpreter provides insight into any 
behavior changes that might occur.

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{method/control-ui.png}
        \caption{Control treatment, no examples}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{method/treatment-ui.png}
        \caption{Experimental treatment, examples}
    \end{subfigure}
    \caption{Each participant received one of the two treatments for the duration of the study.}
\end{figure*}

\section{Results}
% Figures.
\begin{figure*}[ht]
  \centering
  \includegraphics[width=\textwidth]{results/task_points.png}
  \caption{
    Examples did not noticeably affect time-to-completion, except in Task 2
    where the effect is dramatic.
  }
  \label{fig:data-points}
\end{figure*}
% Analysis
\section{Discussion}
